### 2019-02-19 sections/conclusions.tex
fixme
use citet

In this paper we have developed a domain-specific calculus for declarative interactive workflows, named \TOPHAT.
We have shown that our calculus is modular, and clearly seperated from the host language it is embedded in.
By developing this calculus, we have identified the essence of Task-Oriented Programming.
In addition to the formal semantics, we have also demonstrated how to build a user interface from a task description.
We have compared \TOPHAT with workflow moddeling languages, process algebras, functional reactive programming and session types to point out differences and similarities.
Finally, we have proven type safety and progress for our language.

@@

Another form of reasoning about programs is static analysis.
Klinik et al.~\cite{conf/ifl/KlinikJP17} have developed a cost analysis for tasks that require resources in order to be executed.
% Put this line back in for final version of paper: In previous work we have developed a cost analysis for tasks that require resources in order to be executed \cite{conf/ifl/KlinikJP17}.
This analysis was developed for a simpler task calculus, and could be brought over to the one developed here.

% Put this line back in for final version of paper: In other previous work, we have looked at building a generic feedback system for rule-based problems \cite{UUCS2017013}.
Naus et al.~\cite{UUCS2017013} have looked at building a generic feedback system for rule-based problems.
A workflow system typically is rule based, as outlined in their work.
It would be interesting to fit the generic feedback system to \TOPHAT in order to support end-users working in applications developed in this calculus.

>>>>

\fixme{moet passen bij de contributions}
In this paper we have developed a domain-specific calculus for declarative interactive workflows, named \TOPHAT.
We have shown that our calculus is modular, and clearly seperated from the host language it is embedded in.
By developing this calculus, we have identified the essence of Task-Oriented Programming.
In addition to the formal semantics, we have also demonstrated how to build a user interface from a task description.
We have compared \TOPHAT with workflow moddeling languages, process algebras, functional reactive programming and session types to point out differences and similarities.
Finally, we have proven type safety and progress for our language.

@@

Another form of reasoning about programs is static analysis.
\citet{conf/ifl/KlinikJP17} have developed a cost analysis for tasks that require resources in order to be executed.
% Put this line back in for final version of paper: In previous work we have developed a cost analysis for tasks that require resources in order to be executed \cite{conf/ifl/KlinikJP17}.
This analysis was developed for a simpler task calculus, and could be brought over to the one developed here.

% Put this line back in for final version of paper: In other previous work, we have looked at building a generic feedback system for rule-based problems \cite{UUCS2017013}.
\citet{UUCS2017013} have looked at building a generic feedback system for rule-based problems.
A workflow system typically is rule based, as outlined in their work.
It would be interesting to fit the generic feedback system to \TOPHAT in order to support end-users working in applications developed in this calculus.
